% Weekly Outline Example
% Materials - Video 2
% Copyright (c) 2017 Brian R. Hall

\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[pdftex]{graphicx}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{hyperref}
\pagestyle{plain}
\setlength\parindent{0pt}

\begin{document}

\textbf {\large Tentative Course Outline}:

The weekly coverage might change as it depends on the progress of the class.

\begin{table}[h!]
\small
\begin{tabular}{ | c | c | }
\hline
\textbf{Week} & \textbf{Content} \\
\hline
Week 1 & \begin{minipage}{.85\textwidth}
\begin{itemize} \itemsep-0.4em
	\vspace{1mm}
	\item Syllabus, Chapter 1: Language and Data Fundamentals
	\item Activity: Chapter 1 Activity (Number Systems); Assignment 1 (Fundamentals)
	\vspace{1mm}
\end{itemize}
\end{minipage} \\
\hline
Week 2 & \begin{minipage}{.85\textwidth}
\begin{itemize} \itemsep-0.4em
	\vspace{1mm}
	\item Chapter 2: Processor and System Architecture
	\item Activity: Clocks and Cycles; Assignment 2 (x86/x86-64 Architecture)
	\vspace{1mm}
\end{itemize}
\end{minipage} \\
\hline
Week 3 & \begin{minipage}{.85\textwidth}
\begin{itemize} \itemsep-0.4em
	\vspace{1mm}
	\item Chapter 3: Assembly and Syntax Fundamentals
	\item Activity: Syntax Translation; Assignment 3 (Program 1)
	\vspace{1mm}
\end{itemize}
\end{minipage} \\
\hline
Week 4 & \begin{minipage}{.85\textwidth}
\begin{itemize} \itemsep-0.4em
	\vspace{1mm}
	\item Chapter 4: Basic Instructions
	\item Activity: Chapter 4 Questions; Assignment 4 (Program 2)
	\vspace{1mm}
\end{itemize}
\end{minipage} \\
\hline
Week 5 & \begin{minipage}{.85\textwidth}
\begin{itemize} \itemsep-0.4em
	\vspace{1mm}
	\item Chapter 5: Intermediate Instructions
	\item Activity: Chapter 5 Questions; Assignment 5 (Program 3)
	\vspace{1mm}
\end{itemize}
\end{minipage} \\
\hline
Week 6 & \begin{minipage}{.85\textwidth}
\begin{itemize} \itemsep-0.4em
	\vspace{1mm}
	\item Chapter 6: Functions
	\item Activity: Linking Assembly and C++; Assignment 6 (Program 4)
	\vspace{1mm}
\end{itemize}
\end{minipage} \\
\hline
Week 7 & \begin{minipage}{.85\textwidth}
\begin{itemize} \itemsep-0.4em
	\vspace{1mm}
	\item Chapter 12: Hardware and Electrical Components
	\item Activity: Arduinos*; Assignment 7 (Chapter 12 Questions)
	\vspace{1mm}
\end{itemize}
\end{minipage} \\
\hline
Week 8 & \begin{minipage}{.85\textwidth}
\begin{itemize} \itemsep-0.4em
	\vspace{1mm}
	\item Chapter 7: String Instructions and Structures
	\item Midterm Exam
	\vspace{1mm}
\end{itemize}
\end{minipage} \\
\hline
Break & \begin{minipage}{.85\textwidth}
\end{minipage} \\
\hline
Week 9 & \begin{minipage}{.85\textwidth}
\begin{itemize} \itemsep-0.4em
	\vspace{1mm}
	\item Chapter 8: Floating Point Operations
	\item Activity: Chapter 8 Questions; Assignment 8: (Program 5)
	\vspace{1mm}
\end{itemize}
\end{minipage} \\
\hline
Week 10 & \begin{minipage}{.85\textwidth}
\begin{itemize} \itemsep-0.4em
	\vspace{1mm}
	\item Chapter 9: Inline Assembly and Macros
	\item Activity: Chapter 9 Questions; Assignment 9 (Program 6)
	\item Research 1 - Project (one page)
	\vspace{1mm}
\end{itemize}
\end{minipage} \\
\hline
Week 11 & \begin{minipage}{.85\textwidth}
\begin{itemize} \itemsep-0.4em
	\vspace{1mm}
	\item Chapter 11: Other Architectures
	\item Activity: Chapter 11 Questions; Assignment 10 (CPU Architecture Report)
	\vspace{1mm}
\end{itemize}
\end{minipage} \\
\hline
Week 12 & \begin{minipage}{.85\textwidth}
\begin{itemize} \itemsep-0.4em
	\vspace{1mm}
	\item Chapter 10: Advanced Processor and System Architecture
	\item Activity: Chapter 10 Questions; Assignment 11 (Program 7)
	\vspace{1mm}
\end{itemize}
\end{minipage} \\
\hline
Week 13 & \begin{minipage}{.85\textwidth}
\begin{itemize} \itemsep-0.4em
	\vspace{1mm}
	\item Research 2 - Project; Presentations
	\vspace{1mm}
\end{itemize}
\end{minipage} \\
\hline
Week 14 & \begin{minipage}{.85\textwidth}
\begin{itemize} \itemsep-0.4em
	\vspace{1mm}
	\item Research 2 - Project; Presentations
	\vspace{1mm}
\end{itemize}
\end{minipage} \\
\hline
Week 15 & \begin{minipage}{.85\textwidth}
\begin{itemize} \itemsep-0.4em
	\vspace{1mm}
	\item Final Exam
	\vspace{1mm}
\end{itemize}
\end{minipage} \\
\hline
\end{tabular} 
\end{table}
*Arduinos: Open source hardware microcontroller boards/kits.  Requires component organization (hardware and electrical components) and programming (C/C++). See: \href{http://www.arduino.cc}{http://www.arduino.cc}

\newpage
\underline {Week 1} \\
\textbf {Assignment 1}: Chapter 1 Questions \\
\textbf {Activity 1}: Chapter 1 Activity \\

\underline {Week 2} \\
\textbf {Assignment 2}: Chapter 2 Questions \\
\textbf {Activity 2}: Questions based on http://pclt.sites.yale.edu/clocks-and-cycles \\

\underline {Week 3} \\
\textbf {Assignment 3}: Choose one of the assignments at the end of Chapter 3.
\begin{itemize} \itemsep -1.5em
	\item Assignments 3.1 and 3.2 are worth 20 points. \\
	\item Assignment 3.4 is worth 20 + 2 extra credit points. \\
	\item Assignment 3.3 is reserved for the Week 3 Activity. \\
	\item ADDITIONAL REQUIREMENT: Comment every line of code to indicate what it does.
\end{itemize}

\textbf {Activity 3}: Assignment 3.3 Syntax Translation \\
The GAS version of the program is in the Assembly Code Repository and in the Chapter 3 text. \\
Translate the AT\&T GAS code into Intel syntax for MASM or NASM.  Use Appendix A: Assembly Syntax Translation as a reference. \\

\underline {Week 4} \\
\textbf {Assignment 4}: Choose one of the assignments at the end of Chapter 4.
\begin{itemize} \itemsep -1.5em
	\item Assignment 4.2 is worth 10 points. \\
	\item Assignment 4.3 is worth 10 + 2 extra credit points. \\
	\item Assignment 4.1 is just for practice and should not be used for this assignment. \\
	\item ADDITIONAL REQUIREMENT: Comment every line of code to indicate what it does.
\end{itemize}

\textbf {Activity 4a}: Chapter 4 Questions \\
\textbf {Activity 4b}: Review Appendix C: Disassembly. \\
Write Program 4.4. Then, refer to Appendix B: Environment Setup to create a listing file for the program.
Be prepared to show the listing file to the instructor when completed. \\

\underline {Week 5} \\
\textbf {Assignment 5}: Choose one of the assignments at the end of Chapter 5.
\begin{itemize} \itemsep -1.5em
	\item Assignments 5.1 and 5.2 are worth 20 points. \\
	\item Assignment 5.3 should not be used for this assignment. \\
\textbf {Alternative Assignments}: \\
		\item Alternate 1 - Greatest Common Divisor is worth 20 points \\
		\item Alternate 2 - Pin is worth 20 + 2 extra credit points \\
	\item ADDITIONAL REQUIREMENT: Comment every line of code to indicate what it does.
\end{itemize}

\textbf {Activity 5}: Chapter 5 Questions \\

\newpage

\underline {Week 6} \\
\textbf {Assignment 6}: Choose one of the assignments at the end of Chapter 6.
\begin{itemize} \itemsep -1.5em
	\item Assignment 6.1 is worth 20 points. \\
	\item Assignment 6.2 is worth 20 points. Two extra credit points are possible if you extend the assignment to interpret the eflags bits for relevant computation results (CF, OF, SF, ZF). \\
	\item Assignment 6.3 is worth 20 + 4 extra credit points.  Note: An example of Bubble Sort is in Chapter 1. \\
	\item REQUIREMENT: Create a zipped folder that contains the .asm, .cpp, and .obj/.o files and upload the folder.
\end{itemize}

\textbf {Activity 6}: Follow the directions in Appendix E: Linking Assembly and C++ for your chosen assembler. \\

\underline {Week 7} \\
\textbf {Assignment 7}: Chapter 12 Questions \\
\textbf {Activity 7}: Arduino Activity: experiment with Arduino boards, https://www.arduino.cc \\
\textbf {Activity AVR}: Questions based on the Atmel ATmega 16U4/32U4 micro-controllers \\

\underline {Week 8 - Midterm Exam} \\

\underline {Week 9} \\
\textbf {Assignment 8}: Choose one of the assignments at the end of Chapter 8.
\begin{itemize} \itemsep -1.5em
	\item Assignment 8.1 is worth 20 points. \\
	\item Assignment 8.2 is worth 20 + 2 extra credit points. \\
	\item Assignment 8.3 is worth 20 + 4 extra credit points.
\end{itemize}

\textbf {Activity 8}: Chapter 8 Questions \\

\underline {Week 10} \\
\textbf {Assignment 9}: Choose one of the assignments at the end of Chapter 9.
\begin{itemize} \itemsep -1.5em
	\item Assignments 9.1 and 9.2 are worth 20 points. \\
	\item Assignment 9.3 is worth 20 + 2 extra credit points.
\end{itemize}

\textbf {Activity 9}: Chapter 9 Questions \\
\textbf {Research 1}: A one-page project proposal \\

\underline {Week 11} \\
\textbf {Assignment 10}: Complete Assignment 11.1 from Chapter 11. \\
\textbf {Activity 10}: Chapter 11 Questions \\

\underline {Week 12} \\
\textbf {Assignment 11}: Complete Assignment 10.1 from Chapter 10. \\
\textbf {Activity 11}: Chapter 10 Questions

\end{document}
